---
title: "My Analysis"
format: 
  gfm:
    toc: true
    fig-width: 7
    fig-height: 5
---

## START

This is the beginning of descriptive analysis of the women dataset that is available in R, it shall form part of a journey of a thousand miles:

```{r}
women
```

You can add options to executable code like this

```{r}
str(women)
```

# Descriptive Statistics.

# 

```{r}
df <- data.frame(
  age = 58:72,
  height = c(115, 117, 120, 123, 126, 129, 132, 135, 
            139, 142, 146, 150, 154, 159, 164)
  )
df
```

```{r}
x <- women$height
y <- women$weight

```

```{r}
plot(x,y)
```

```{r}
plot(x, y, type ='l')
```

Barchart

```{r}
barplot(y, names.arg = x)
```

Density plot

```{r}
plot(density(y))
```

Q-Q plot

```{r}
qqnorm(y); qqline(y)
```

Residuals

```{r}
plot(x, resid(lm(y ~ x)))
```

ACF plot

```{r}
acf(y)
```

# Predictions

linear

```{r}
predict(lm(y ~x), data.frame(x =73))
```

```{r}
predict(lm(y ~poly(x,2)), data.frame(x=73))
#quad pred
```

Linear Interpolation

```{r}
approx(x, y, xout = 73)$y
```

Spline Interplolation

```{r}
spline(x, y, xout = 73)$y
```

LOESS

```{r}
#loess(y ~ x) %>% 
 # predict(data.frame(x=73))
```

```{r}
library(randomForest)
predict(randomForest(y ~x, ntree =50), data.frame(x =73))
```

```{r}
t.test(y, mu =140)
```

```{r}
mean(y)
```

# Hypothesis Tests

```{r}
t.test(y[1:7], y[8:15])
```

Test Equal Variances

```{r}
var.test(y[1:7], y[8:15])
```

Wilcoxon For Non-Parametric

```{r}
wilcox.test(y[1:7], y[8:15])
```

Normality Test

```{r}
shapiro.test(y)
```

Distribution Test

```{r}
ks.test(y,"pnorm", mean(y), sd(y))
```

Chi-square Goodness of Fit

```{r}
chisq.test(table(cut(y,3)))

```

```{r}
library(dplyr)
women %>% 
  lm(x ~ y, data =.) %>% 
  summary()
```

F-Test For regression

```{r}
summary(lm(x ~ y))$fstatistic
```

Durbin-Watson Test

```{r}

library(lmtest)
dwtest(lm(x ~y))
```

```{r}
cor(x,y)
```

```{r}
library(readr)
ai_job_replacement_2020_2026_v2 <- read_csv("D:/Desktop/ai_job_replacement_2020_2026_v2.csv")
```

```{r}
str(ai_job_replacement_2020_2026_v2)
```

`{View(ai_job_replacement_2020_2026_v2)}`

```{r}
colSums(is.na(ai_job_replacement_2020_2026_v2))
```

```{r}
names(ai_job_replacement_2020_2026_v2)
```

```{r}

#install.packages(c("tidyverse", "skimr", "GGally", "corrplot"))

# Load packages
library(tidyverse)
library(skimr)
library(GGally)
library(corrplot)
```

```{r}
df <-ai_job_replacement_2020_2026_v2
df
```

```{r}
head(df)
```

```{r}
dim(df)
```

```{r}
summary(df)
```

```{r}
# 3. Check for missing values
colSums(is.na(df))
```

```{r}
# 4. Clean column names
library(tidyverse)

```

```{r}
# 5. Convert categorical variables to factors
df$job_role <- as.factor(df$job_role)
df$industry <- as.factor(df$industry)
df$country <- as.factor(df$country)
df$education_requirement_level <- as.factor(df$education_requirement_level)
```

```{r}
# 6. Check factor levels
levels(df$job_role)[1:20]
levels(df$industry)
levels(df$country)
levels(df$education_requirement_level)
```

```{r}
str(df)
```

```{r}
# 7. Create derived columns
df <- df %>%
  mutate(
    # Year categories
    year_category = case_when(
      year <= 2022 ~ "Past",
      year <= 2024 ~ "Present",
      TRUE ~ "Future"
    ),
    # Risk brackets
    risk_bracket = case_when(
      automation_risk_percent < 33 ~ "Low Risk",
      automation_risk_percent < 67 ~ "Medium Risk",
      TRUE ~ "High Risk"
    )
  )
```

```{r}
# 8. Make them factors
df$year_category <- factor(df$year_category, levels = c("Past", "Present", "Future"))
df$risk_bracket <- factor(df$risk_bracket, levels = c("Low Risk", "Medium Risk", "High Risk"))
```

```{r}
# 9. Quick summary of numerical columns
df %>%
  select(where(is.numeric)) %>%
  summary()
```

```{r}
# 10. Save cleaned data
write.csv(df, "ai_job_replacement_cleaned.csv", row.names = FALSE)

```

## **Descriptive Analysis with Visualizations**

```{r}
# Load visualization libraries
library(ggplot2)
library(viridis)
library(gridExtra)
```

```{r}
# Set theme
theme_set(theme_minimal() + 
          theme(plot.title = element_text(hjust = 0.5, face = "bold"),
                axis.text.x = element_text(angle = 45, hjust = 1)))
```

```{r}
# ============================================
# OBJECTIVE 1 & 2: Job Risk and Salary Trends
# ============================================

# 1.1 Rank jobs by automation risk
job_risk <- df %>%
  group_by(job_role) %>%
  summarise(
    avg_risk = mean(automation_risk_percent),
    avg_salary_change = mean(salary_change_percent),
    count = n()
  ) %>%
  arrange(desc(avg_risk))
```

```{r}
# Top 10 and bottom 10
top_10 <- head(job_risk, 10)
bottom_10 <- tail(job_risk, 10)
```

```{r}
# Combine for plotting
risk_plot_data <- rbind(
  cbind(top_10, category = "Highest Risk"),
  cbind(bottom_10, category = "Lowest Risk")
)
```

```{r}
# Bar plot
ggplot(risk_plot_data, aes(x = reorder(job_role, avg_risk), 
                            y = avg_risk, fill = category)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  scale_fill_manual(values = c("Highest Risk" = "red", "Lowest Risk" = "green")) +
  labs(title = "Jobs with Highest and Lowest Automation Risk",
       x = "Job Role", y = "Average Automation Risk (%)")
```

```{r}
# 1.2 Risk vs Salary Change scatter plot
ggplot(df, aes(x = automation_risk_percent, y = salary_change_percent)) +
  geom_point(alpha = 0.3, color = "blue") +
  geom_smooth(method = "lm", color = "red") +
  labs(title = "Automation Risk vs Salary Change",
       x = "Automation Risk (%)", y = "Salary Change (%)")
```

```{r}
# 1.3 Correlation
cor(df$automation_risk_percent, df$salary_change_percent, use = "complete.obs")
```

```{r}
# 1.4 Box plot by risk bracket
ggplot(df, aes(x = risk_bracket, y = salary_change_percent, fill = risk_bracket)) +
  geom_boxplot() +
  scale_fill_manual(values = c("Low Risk" = "green", "Medium Risk" = "orange", "High Risk" = "red")) +
  labs(title = "Salary Change by Risk Category", x = "Risk Category", y = "Salary Change (%)") +
  theme(legend.position = "none")
```

```{r}
# ============================================
# OBJECTIVE 3: Industry and Country Vulnerability
# ============================================

# 3.1 Industry summary
industry_summary <- df %>%
  group_by(industry) %>%
  summarise(
    avg_risk = mean(automation_risk_percent),
    avg_ai_score = mean(ai_replacement_score),
    avg_adoption = mean(ai_adoption_level),
    count = n()
  ) %>%
  arrange(desc(avg_risk))
```

```{r}
industry_summary
```

```{r}
# Industry bar plot
ggplot(industry_summary, aes(x = reorder(industry, avg_risk), y = avg_risk)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  labs(title = "Industry Vulnerability to AI", x = "Industry", y = "Avg Automation Risk (%)")
```

```{r}
# 3.2 Country summary
country_summary <- df %>%
  group_by(country) %>%
  summarise(
    avg_risk = mean(automation_risk_percent),
    avg_ai_score = mean(ai_replacement_score),
    avg_adoption = mean(ai_adoption_level),
    count = n()
  ) %>%
  arrange(desc(avg_risk))

# View
country_summary
```

```{r}
# Country bar plot
ggplot(country_summary, aes(x = reorder(country, avg_risk), y = avg_risk)) +
  geom_bar(stat = "identity", fill = "darkred") +
  coord_flip() +
  labs(title = "Country Vulnerability to AI", x = "Country", y = "Avg Automation Risk (%)")
```

```{r}
# Country bar plot
ggplot(country_summary, aes(x = reorder(country, avg_risk), y = avg_risk)) +
  geom_bar(stat = "identity", fill = "darkred") +
  coord_flip() +
  labs(title = "Country Vulnerability to AI", x = "Country", y = "Avg Automation Risk (%)")

# 3.3 Simple heatmap of top industries and countries
# Get top 5 industries and countries
top_industries <- head(industry_summary$industry, 5)
top_countries <- head(country_summary$country, 5)

# Filter data
heatmap_data <- df %>%
  filter(industry %in% top_industries, country %in% top_countries) %>%
  group_by(industry, country) %>%
  summarise(avg_risk = mean(automation_risk_percent), .groups = "drop")
```

```{r}
# Simple heatmap
ggplot(heatmap_data, aes(x = country, y = industry, fill = avg_risk)) +
  geom_tile() +
  scale_fill_gradient(low = "white", high = "red") +
  labs(title = "Automation Risk: Top Industries vs Countries", fill = "Risk %")
```

```{r}
# ============================================
# OBJECTIVE 4: Reskilling Gap
# ============================================

# 4.1 Skill gap vs reskilling urgency
ggplot(df, aes(x = skill_gap_index, y = reskilling_urgency_score)) +
  geom_point(alpha = 0.3, color = "purple") +
  geom_smooth(method = "lm", color = "black") +
  labs(title = "Skill Gap vs Reskilling Urgency",
       x = "Skill Gap Index", y = "Reskilling Urgency")
```

```{r}
# Correlation
cor(df$skill_gap_index, df$reskilling_urgency_score, use = "complete.obs")
```

```{r}
# 4.2 Jobs with highest reskilling urgency
top_reskilling <- df %>%
  group_by(job_role) %>%
  summarise(
    urgency = mean(reskilling_urgency_score),
    risk = mean(automation_risk_percent)
  ) %>%
  arrange(desc(urgency)) %>%
 head(15)
```

```{r}
# Plot
ggplot(top_reskilling, aes(x = reorder(job_role, urgency), y = urgency, fill = risk)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  scale_fill_gradient(low = "yellow", high = "red") +
  labs(title = "Top 15 Jobs Requiring Urgent Reskilling",
       x = "Job Role", y = "Reskilling Urgency", fill = "Risk %")
```

```{r}
# ============================================
# OBJECTIVE 5: Remote Work as Mitigating Factor
# ============================================

# 5.1 Remote feasibility vs automation risk
ggplot(df, aes(x = remote_feasibility_score, y = automation_risk_percent)) +
  geom_point(alpha = 0.3, color = "darkgreen") +
  geom_smooth(method = "lm", color = "red") +
  labs(title = "Remote Feasibility vs Automation Risk",
       x = "Remote Feasibility Score", y = "Automation Risk (%)")
```

```{r}
# Correlation
cor(df$remote_feasibility_score, df$automation_risk_percent, use = "complete.obs")

```

```{r}
# 5.2 Remote feasibility by industry
ggplot(df, aes(x = reorder(industry, remote_feasibility_score, FUN = median), 
               y = remote_feasibility_score)) +
  geom_boxplot(fill = "lightblue") +
  coord_flip() +
  labs(title = "Remote Feasibility by Industry",
       x = "Industry", y = "Remote Feasibility Score")
```

```{r}
# ============================================
# OBJECTIVE 6: Educational Requirements
# ============================================

# 6.1 Automation risk by education level
ggplot(df, aes(x = education_requirement_level, y = automation_risk_percent)) +
  geom_boxplot(fill = "orange") +
  labs(title = "Automation Risk by Education Level",
       x = "Education Level (1=Lowest, 5=Highest)", y = "Automation Risk (%)")
```

```{r}
# 6.2 Salary by education level
ggplot(df, aes(x = education_requirement_level, y = salary_before_usd / 1000)) +
  geom_boxplot(fill = "steelblue") +
  labs(title = "Salary by Education Level",
       x = "Education Level (1=Lowest, 5=Highest)", y = "Salary (thousands USD)")
```

```{r}
# 6.3 Summary table
edu_summary <- df %>%
  group_by(education_requirement_level) %>%
  summarise(
    avg_risk = mean(automation_risk_percent),
    avg_salary = mean(salary_before_usd),
    avg_salary_change = mean(salary_change_percent),
    count = n()
  )
```

```{r}
# View
edu_summary
```

## **Simple Predictive Models**

```{r}
# Load modeling libraries
library(randomForest)
#library(caret)
set.seed(123)
```

```{r}
# ============================================
# OBJECTIVE 7: Predicting Salary Change
# ============================================

# Prepare data
model_df <- df %>%
  select(job_role, industry, country, year,
         automation_risk_percent, ai_replacement_score,
         skill_gap_index, salary_before_usd,
         remote_feasibility_score, ai_adoption_level,
         education_requirement_level, salary_change_percent) %>%
  na.omit()
```

```{r}
# Split data
set.seed(123)
train_idx <- sample(1:nrow(model_df), 0.7 * nrow(model_df))
train <- model_df[train_idx, ]
test <- model_df[-train_idx, ]
```

```{r}
# Simple Random Forest model
rf_salary <- randomForest(
  salary_change_percent ~ .,
  data = train,
  ntree = 100,
  importance = TRUE
)
```

```{r}
# Predictions
predictions <- predict(rf_salary, test)
```

```{r}
# Calculate RMSE (Root Mean Square Error)
rmse <- sqrt(mean((predictions - test$salary_change_percent)^2))
print(paste("RMSE:", round(rmse, 3)))
```

```{r}
# Calculate R-squared
ss_res <- sum((test$salary_change_percent - predictions)^2)
ss_tot <- sum((test$salary_change_percent - mean(test$salary_change_percent))^2)
r2 <- 1 - (ss_res / ss_tot)
print(paste("R-squared:", round(r2, 3)))
```

```{r}
# Feature importance
importance_df <- data.frame(
  feature = rownames(importance(rf_salary)),
  importance = importance(rf_salary)[, "%IncMSE"]
) %>%
  arrange(desc(importance))
```

```{r}
# Plot top 10 features
head(importance_df, 10) %>%
  ggplot(aes(x = reorder(feature, importance), y = importance)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  labs(title = "Top Factors Affecting Salary Change",
       x = "Feature", y = "Importance")
```

```{r}
# ============================================
# OBJECTIVE 8: Classifying Job Risk
# ============================================

# Create classification dataset
class_df <- df %>%
  select(job_role, industry, country, year,
         ai_replacement_score, skill_gap_index,
         remote_feasibility_score, ai_adoption_level,
         education_requirement_level, risk_bracket) %>%
  na.omit()
```

```{r}
# Split
set.seed(123)
train_idx_c <- sample(1:nrow(class_df), 0.7 * nrow(class_df))
train_c <- class_df[train_idx_c, ]
test_c <- class_df[-train_idx_c, ]
```

```{r}
# Random Forest Classifier
rf_class <- randomForest(
  risk_bracket ~ .,
  data = train_c,
  ntree = 100,
  importance = TRUE
)
```

```{r}
# Predictions
pred_class <- predict(rf_class, test_c)
```

```{r}
# Confusion Matrix
table(Predicted = pred_class, Actual = test_c$risk_bracket)
```

```{r}
# Accuracy
accuracy <- mean(pred_class == test_c$risk_bracket)
print(paste("Accuracy:", round(accuracy, 3)))
```

```{r}
# Feature importance for classification
class_imp <- data.frame(
  feature = rownames(importance(rf_class)),
  importance = importance(rf_class)[, "MeanDecreaseGini"]
) %>%
  arrange(desc(importance))
```

```{r}
# Plot
head(class_imp, 10) %>%
  ggplot(aes(x = reorder(feature, importance), y = importance)) +
  geom_bar(stat = "identity", fill = "darkgreen") +
  coord_flip() +
  labs(title = "Top Factors for Predicting Risk Category",
       x = "Feature", y = "Importance")
```

```{r}
# ============================================
# OBJECTIVE 9: Predicting Reskilling Urgency
# ============================================

# Similar to Objective 7 but with different target
urgency_df <- df %>%
  select(job_role, industry, country, year,
         automation_risk_percent, ai_replacement_score,
         skill_gap_index, remote_feasibility_score,
         ai_adoption_level, education_requirement_level,
         reskilling_urgency_score) %>%
  na.omit()
```

```{r}
# Split
set.seed(123)
train_idx_u <- sample(1:nrow(urgency_df), 0.7 * nrow(urgency_df))
train_u <- urgency_df[train_idx_u, ]
test_u <- urgency_df[-train_idx_u, ]
```

```{r}
# Random Forest for urgency
rf_urgency <- randomForest(
  reskilling_urgency_score ~ .,
  data = train_u,
  ntree = 100,
  importance = TRUE
)
```

```{r}
# Predictions
pred_urgency <- predict(rf_urgency, test_u)
```

```{r}
# RMSE
rmse_u <- sqrt(mean((pred_urgency - test_u$reskilling_urgency_score)^2))
print(paste("Reskilling Urgency RMSE:", round(rmse_u, 3)))
```

```{r}
# Feature importance
urgency_imp <- data.frame(
  feature = rownames(importance(rf_urgency)),
  importance = importance(rf_urgency)[, "%IncMSE"]
) %>%
  arrange(desc(importance))
```

```{r}
# Plot
head(urgency_imp, 10) %>%
  ggplot(aes(x = reorder(feature, importance), y = importance)) +
  geom_bar(stat = "identity", fill = "purple") +
  coord_flip() +
  labs(title = "Top Factors Affecting Reskilling Urgency",
       x = "Feature", y = "Importance")
```

## **Advanced Analysis**

```{r}
# ============================================
# OBJECTIVE 10: Temporal Analysis
# ============================================

# Yearly trends
yearly <- df %>%
  group_by(year) %>%
  summarise(
    risk = mean(automation_risk_percent),
    adoption = mean(ai_adoption_level),
    ai_score = mean(ai_replacement_score),
    salary_change = mean(salary_change_percent)
  )
```

```{r}
# Plot multiple trends
par(mfrow = c(2, 2))
plot(yearly$year, yearly$risk, type = "b", col = "red", 
     xlab = "Year", ylab = "Risk %", main = "Automation Risk Trend")
plot(yearly$year, yearly$adoption, type = "b", col = "blue",
     xlab = "Year", ylab = "Adoption Level", main = "AI Adoption Trend")
plot(yearly$year, yearly$ai_score, type = "b", col = "green",
     xlab = "Year", ylab = "AI Score", main = "AI Replacement Score Trend")
plot(yearly$year, yearly$salary_change, type = "b", col = "purple",
     xlab = "Year", ylab = "Salary Change %", main = "Salary Change Trend")
par(mfrow = c(1, 1))
```

```{r}
# Trends by country (top 5 countries)
top_countries <- names(sort(table(df$country), decreasing = TRUE)[1:5])

df %>%
  filter(country %in% top_countries) %>%
  group_by(country, year) %>%
  summarise(avg_risk = mean(automation_risk_percent), .groups = "drop") %>%
  ggplot(aes(x = year, y = avg_risk, color = country, group = country)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  labs(title = "Automation Risk Trends by Country",
       x = "Year", y = "Avg Risk (%)")
```

```{r}
# ============================================
# OBJECTIVE 11: Simple Cluster Analysis
# ============================================

# Prepare job-level data
job_data <- df %>%
  group_by(job_role) %>%
  summarise(
    risk = mean(automation_risk_percent),
    ai_score = mean(ai_replacement_score),
    skill_gap = mean(skill_gap_index),
    remote = mean(remote_feasibility_score),
    urgency = mean(reskilling_urgency_score),
    count = n()
  ) %>%
  filter(count > 10)  # Only jobs with enough data
```

```{r}
# Scale the data
job_scaled <- scale(job_data[, c("risk", "ai_score", "skill_gap", "remote", "urgency")])
```

```{r}
# Try 3 clusters
set.seed(123)
kmeans_result <- kmeans(job_scaled, centers = 3, nstart = 25)
```

```{r}
# Add cluster to data
job_data$cluster <- as.factor(kmeans_result$cluster)
```

```{r}
# View cluster characteristics
job_data %>%
  group_by(cluster) %>%
  summarise(
    avg_risk = mean(risk),
    avg_ai_score = mean(ai_score),
    avg_skill_gap = mean(skill_gap),
    avg_remote = mean(remote),
    avg_urgency = mean(urgency),
    count = n()
  )
```

```{r}
# Visualize clusters (using first two principal components)
pca <- prcomp(job_scaled)
plot_data <- data.frame(
  PC1 = pca$x[, 1],
  PC2 = pca$x[, 2],
  cluster = job_data$cluster,
  job = job_data$job_role
)

ggplot(plot_data, aes(x = PC1, y = PC2, color = cluster, label = job)) +
  geom_point(size = 3) +
  #geom_text_repel(size = 2, max.overlaps = 5) +
  labs(title = "Job Clusters Based on AI Risk Factors") +
  theme(legend.position = "bottom")
```

```{r}
# ============================================
# OBJECTIVE 12: The AI Paradox
# ============================================

# Industry-level analysis
industry_paradox <- df %>%
  group_by(industry) %>%
  summarise(
    adoption = mean(ai_adoption_level),
    risk = mean(automation_risk_percent),
    count = n()
  )

```

```{r}
# Scatter plot
ggplot(industry_paradox, aes(x = adoption, y = risk, label = industry)) +
  geom_point(size = 4, aes(color = count)) +
  #geom_text_repel() +
  scale_color_gradient(low = "blue", high = "red") +
  labs(title = "AI Paradox: Adoption vs Risk by Industry",
       x = "Average AI Adoption Level", y = "Average Automation Risk (%)",
       color = "Sample Size") +
  geom_smooth(method = "lm", se = FALSE, color = "gray", linetype = "dashed")
```

```{r}
# Correlation
cor(industry_paradox$adoption, industry_paradox$risk)
```

```{r}
# ============================================
# OBJECTIVE 13: Globalization of AI Risk
# ============================================

# Select a few common job roles
common_jobs <- c("Software Engineer", "Data Analyst", "Teacher", 
                 "Financial Analyst", "Customer Support Rep")

# Filter data
job_country <- df %>%
  filter(job_role %in% common_jobs) %>%
  group_by(job_role, country) %>%
  summarise(avg_risk = mean(automation_risk_percent), .groups = "drop")
```

```{r}
# Create bar plot
ggplot(job_country, aes(x = country, y = avg_risk, fill = job_role)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Automation Risk by Country for Selected Jobs",
       x = "Country", y = "Average Automation Risk (%)", fill = "Job Role") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}
# Alternative: heatmap
job_country_matrix <- job_country %>%
  pivot_wider(names_from = country, values_from = avg_risk, values_fill = 0)

job_country_matrix %>%
  pivot_longer(-job_role, names_to = "country", values_to = "risk") %>%
  ggplot(aes(x = country, y = job_role, fill = risk)) +
  geom_tile() +
  scale_fill_gradient(low = "white", high = "red") +
  labs(title = "Heatmap of AI Risk: Jobs vs Countries",
       x = "Country", y = "Job Role", fill = "Risk %")
```

```{r}
# ============================================
# FINAL SUMMARY: Key Insights
# ============================================

# Create a simple summary of the most important findings
```

```{r}
# 1. Most and least risky jobs
most_risky <- head(job_risk$job_role, 3)
least_risky <- tail(job_risk$job_role, 3)

# 2. Most vulnerable industries
top_risky_industries <- head(industry_summary$industry, 3)

# 3. Most vulnerable countries
top_risky_countries <- head(country_summary$country, 3)

# 4. Education and risk
edu_risk_correlation <- cor(as.numeric(df$education_requirement_level), 
                            df$automation_risk_percent, use = "complete.obs")
```

```{r}
# Print summary
print("=== KEY INSIGHTS ===")
print(paste("Most risky jobs:", paste(most_risky, collapse = ", ")))
print(paste("Least risky jobs:", paste(least_risky, collapse = ", ")))
print(paste("Most vulnerable industries:", paste(top_risky_industries, collapse = ", ")))
print(paste("Most vulnerable countries:", paste(top_risky_countries, collapse = ", ")))
print(paste("Education vs Risk correlation:", round(edu_risk_correlation, 3)))
print(paste("Remote work reduces risk (correlation):", 
            round(cor(df$remote_feasibility_score, df$automation_risk_percent), 3)))
print(paste("Higher skill gap = higher reskilling urgency (correlation):",
            round(cor(df$skill_gap_index, df$reskilling_urgency_score), 3)))
```
